Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
Edit experiments section

Experiments are carried out using temporal-scattering coefficients as well as Mel Frequency Cesptral Coefficients (MFCCs) as features. For the temporal-scattering, each scene is described by 128 vectors of scattering coefficients, with half-overlapping windows $\boldsymbol{\phi}(t)$ of duration $T=188\,\mathrm{ms}$. Experiments are conducted with and without the logarithmic compression (see Section \ref{sec:logcomp}).

Different sets of parameters were tested to compute the MFCCs. Results here are only reported for the best setting. 40 MFCCs (including the first energy coefficient) are computed for windows of 50ms and hops of 25ms, with a full frequency range. This setting gives us 600 feature vectors per scenes. It has been reported that classifying the full set of frames directly may not be the best approach \cite{rakotomamonjy2015histogram}. In order to reduce the data dimensionality, a pooling step is performed on the MFCCs vectors: each set of MFCCs vectors is divided into $n$ non-overlapping $t$-seconds long "texture" windows. Each $n$ texture windows are then averaged over time. As the \emph{ob} approaches involve a clustering step, it is desirable to ensure that each scene is described by circa the same number of vectors prior to the clustering step, for both the temporal-scattering and the MFCCs. Thus, $t$ is set to 250ms, resulting in 120 MFCCs texture windows per scene.

@@

The influence of the temporal-scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (\emph{i.e.} ASSR) and in a supervised setting (\emph{i.e.} ASC).

For the ASSR setting, evaluation is performed on the private dataset of the DCASE 2013 challenge. The metric used is the precision at rank $k$ ($p@k$), which is the  average  number  of  items  of  the  same  class among the $k$ closest items averaged for all possible seed items. The $p@k$ is computed for $k=[1,\ldots,9]$, $9$ being the number of elements that are of the same class than the seed item. Note that a $p@1$ is equivalent to an accuracy computed based on the labels of the 1st nearest neighbors of the items to classify. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameter $N$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$.

For the ASC setting, the systems are evaluated  with five-fold  stratified cross validation on the private dataset of the DCASE 2013 challenge. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public dataset of the DCASE 2013 challenge, using five-fold  stratified cross validation as well. Clustering is done using an enhanced version of the popular K-means algorithm known as $K$-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points.

The \emph{ob} approaches are compared to commonly used approaches using an early integration strategy (\emph{early}) for the ASSR setting, and both an early and a late integration (\emph{late}) strategy for the ASC setting (see Section \ref{sec:eili}). In thsi context early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions.

As most of the 2013 DCASE challenge participants did, a Support Vector Machine (SVM), which is a large-margin binary discriminators with tunable regularization of misclassified examples, is used as classifier for the ASC setting. The parameter $C$ is here set to one.

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{early} and \emph{late} approaches, a linear kernel as well as a RBF kernel are used. As for the \emph{ob} approaches, the RBF kernel is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, being frames, texture windows or centroids are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test set splits of the cross validation scheme (see Section \ref{sec:stand}).

>>>>

Experiments are carried out using temporal scattering coefficients as well as mel-frequency cepstral coefficients (MFCCs) as features. For the temporal scattering, each scene is described by $128$ vectors of scattering coefficients computed with half-overlapping windows $\boldsymbol{\phi}(t)$ of duration $T=188\,\mathrm{ms}$. Experiments are conducted with and without the logarithmic compression (see Section \ref{sec:logcomp}).

Different sets of parameters were tested to compute the MFCCs. Results here are only reported for the best setting, which consisted of $40$ MFCCs (including the first energy coefficient) computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. This setting gives us $600$ feature vectors per scene. It has been reported that classifying the each individual frame directly may not be the best approach \cite{rakotomamonjy2015histogram}. \ja{Why?} In order to reduce the amount of data, a pooling step is performed on the MFCCs: each recording is divided into $n$ non-overlapping $t$-seconds long ``texture'' windows. The MFCC vectors within each texture window are then averaged in time. As the \emph{ob} approaches involve a clustering step, we need to ensure that both MFCCs and scattering coefficients have a comparable number of vectors per recording. \ja{Why do we need to do this?} Thus, $t$ is set to $250\,\mathrm{ms}$, resulting in $120$ MFCCs texture windows per scene.

\ja{We've tested the impact of the logarithm here, but not of the feature selection or standardization. Should we do this as well? For the feature selection, we did say earlier that we would test its impact.}

@@

The influence of the temporal scattering transform and the \emph{ob} approaches are assessed in an unsupervised setting (ASSR) and in a supervised setting (ASC).

For ASSR, evaluation is performed on the private part of the DCASE2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averagin over all query items. The $p@k$ is computed for $k=\{1,\ldots,9\}$, since each class only has $10$ items \ja{?}. Note that a $p@1$ is equivalent to the classification accuracy obtained by choosing the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameter $N$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. \ja{I'm not sure what this means. Do we fix $m$ and $N$ here for all experiments or do we optimize them over the test data each time? If so, this will bias the results, no?}

For ASC, the systems are again evaluated on the private part of DCASE2013, but here with five-fold stratified cross validation. The folds are identical to those used in the original challenge. Optimal parameters (see above) are this time learned on the public part of the DCASE2013 dataset, also using five-fold stratified cross validation. Clustering is done using an enhanced version of the popular K-means algorithm known as $K$-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. \ja{How are they selected differently?}

The \emph{ob} approaches are compared to commonly used early integration approach (\emph{early}) for ASSR, while both early and late integration (\emph{late}) strategy are evaluated for the ASC setting (see Section \ref{sec:eili}). In this context early integration refers to an averaging of the features and late integration refers to a majority voting of the predictions. \ja{We should perhaps mention this in that particular section instead of over here.}

In the same way as the majority of the DCASE2013 participants, we use an SVM for the ASC task, which is a large-margin binary discriminator with tunable regularization of misclassified examples. The parameter $C$ is here set to $1$.

For the \emph{ob} approaches, we use the precomputed kernels described in Section \ref{sec:object}. For both the \emph{early} and \emph{late} approaches, a linear kernel as well as a RBF kernel are used. As in the RBF kernels used in the \emph{ob} approaches, the RBF kernel in the SVM is scaled locally using the method proposed in \cite{selfTuneManor2004}. All feature vectors, be they frames, texture windows or centroids, are standardized prior to be given to the classifier. The standardization is computed with respect to the train/test splits of the cross validation scheme (see Section \ref{sec:stand}).
